Anomalous waves triggered by abrupt depth changes: experimental measurements and deterministic-statistical truncated KdV theory

### 2019-10-07 paper2_JNLS/paper.tex
NM

	The right column of Fig.~\ref{ExpSpatialStats}

>>>>

	To complement the displacement statistics, we report here statistics for the surface slope $\eta_x$ in the right column of Fig.~\ref{ExpSpatialStats}. Our attention to slope statistics was motivated by new theoretical developments by Majda et al.~\cite{majda2019}. The surface slope is extracted from the experimental images through numerical differentiation of the free surface using Savitzky-Golay methods. This ability to extract surface slope is another advantage of optical measurements over discrete probes.
